Fifteen years of decentralization attempts

### 2014-03-18 paper.tex
Fixed some small typos

	\subsection{Tribler} % 2008
		Tribler is a social-based peer-to-peer file sharing system based on the bittorrent protocol. \cite{pouwelse2008tribler}. Tribler considers social phenomena and the sense of community as important parts of file sharing. Although the system is completely decentralized, it does not yet provide its users with anonymity. However, this is something that is currently undergoing research.

		Tribler introduces a novel protocol called buddycast. Peer and content discovery use this protocol, which disseminates information epidemically. Additionally, the protocol allows users to find taste buddies, which are peers that share similar interests in files. This enables quick finding of content that a user is interested in and builds on the idea of social phenomena.

		Although not an anonymization network, Tribler does accomplish a lot on decentralization. The buddycast protocol uses bittorrent infohashes to spread information completely decentralized throughout the network. With future work on anonymization this can be a promising approach to anonymous file sharing.

>>>>

	\subsection{Tribler} % 2008
		Tribler is a social-based peer-to-peer file sharing system based on the BiTtorrent protocol. \cite{pouwelse2008tribler}. Tribler considers social phenomena and the sense of community as important parts of file sharing. Although the system is completely decentralized, it does not yet provide its users with anonymity. However, this is something that is currently undergoing research.

		Tribler introduces a novel protocol called BuddyCast. Peer and content discovery use this protocol, which disseminates information epidemically. Additionally, the protocol allows users to find taste buddies, which are peers that share similar interests in files. This enables quick finding of content that a user is interested in and builds on the idea of social phenomena.

		Although not an anonymization network, Tribler does accomplish a lot on decentralization. The BuddyCast protocol uses BitTorrent infohashes to spread information completely decentralized throughout the network. With future work on anonymization, this can be a promising approach to anonymous file sharing.
